Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
improve pictures

The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of the latter.
The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
Since then, the associahedron has been largely ``demystified'' with several polytopal constructions and generalizations (further references are discussed below).
Its realizations can be classified into three species: the secondary polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, the $\b{g}$-vectors realizations~\cite{Loday, HohlwegLange, LangePilaud, HohlwegLangeThomas, HohlwegPilaudStella, Postnikov, PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the $\b{d}$-vector realizations~\cite{ChapotonFominZelevinsky, CeballosSantosZiegler}. See~\cite{CeballosSantosZiegler} for a discussion of these realizations and their connections.

>>>>

The associahedron is a ``mythical polytope'' \cite{Haiman} whose facial structure encodes Catalan families: its vertices correspond to parenthesizations of a non-associative product, triangulations of a convex polygon, or binary trees; its edges correspond to applications of the associativity rule, diagonal flips, or edge rotations; and in general its faces correspond to partial parenthesizations, diagonal dissections, or Schr\"oder trees.
Its combinatorial and topological structure was introduced in early works of D.~Tamari~\cite{Tamari} and J.~Stasheff~\cite{Stasheff}, and a first polytopal model was realized by J.~Milnor for the PhD defense of the latter.
The first systematic polytopal realizations were constructed by M.~Haiman~\cite{Haiman} and C.~Lee~\cite{Lee}.
Since then, the associahedron has been largely ``demystified'' with several polytopal constructions and generalizations (some are discussed below).
Its realizations can be classified into three species: the secondary polytopes~\cite{GelfandKapranovZelevinsky, BilleraFillimanSturmfels}, the $\b{g}$-vectors realizations~\cite{Loday, HohlwegLange, LangePilaud, HohlwegLangeThomas, HohlwegPilaudStella, Postnikov, PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and the $\b{d}$-vector realizations~\cite{ChapotonFominZelevinsky, CeballosSantosZiegler}. See~\cite{CeballosSantosZiegler} for a discussion of these realizations and their connections.
